Timing and magnitude of climate driven range shifts in transboundary fish stocks challenge their management

### 2021-05-26 Scripts/Supplements.Rmd
Changed title

---
title: "Supplementary Materials for Imminent range shifts in transboundary fish stocks challenge their management under climate change"
author: 'Juliano Palacios-Abrantes, Thomas L. Frölicher, Gabriel Reygondeau, U. Rashid Sumaila, Alessandro Tagliabue, Colette C.C. Wabnitz, and William W.L. Cheung'
output:
  bookdown::word_document2:
    toc : no
    keep_tex: no
    number_sections: yes
reference_docx: ../References/supplementary_template.docx
bibliography: ../References/ToE_Ref.bib
csl: ../References/science.csl
header-includes:
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H} #make every figure with caption = h
- \floatplacement{table}{H}
- \usepackage{caption}
- \captionsetup[figure]{name = Figure S}
- \captionsetup[table]{name = Table S}
---

>>>>

---
title: "Timing and magnitude of climate driven range shifts in transboundary fish stocks challenge their management"
author: 'Juliano Palacios-Abrantes, Thomas L. Frölicher, Gabriel Reygondeau, U. Rashid Sumaila, Alessandro Tagliabue, Colette C.C. Wabnitz, and William W.L. Cheung'
output:
  bookdown::word_document2:
    toc : no
    keep_tex: no
    number_sections: yes
reference_docx: ../References/supplementary_template.docx
bibliography: ../References/ToE_Ref.bib
csl: ../References/science.csl
header-includes:
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H} #make every figure with caption = h
- \floatplacement{table}{H}
- \usepackage{caption}
- \captionsetup[figure]{name = Figure S}
- \captionsetup[table]{name = Table S}
---
